\begin{center}
       \Large
       \textbf{ABSTRACT} \\
        \vspace{1.5cm}
        \large
        \textbf{Semi-empirical Thermal Modelling of LAPAN-A3 Satellite Using Machine Learning Method}\\
        
        \vspace{1.5cm}
        
        by\\
        Ricky Sutardi\\
        NIM : 13617051\\
        (Bachelor's Program in Aerospace Engineering)\\
        \vspace{1.5cm}
\end{center}

From the satellite temperature sensor readings, it is found that LAPAN-A3, an
Indonesian microsatellite, requires special maneuver to keep its main payload,
a multispectral imager, above 0 \degree C. It can then be concluded that the
satellite passive thermal control system is inadequate for the satellite
mission needs. To prevent this problem in future satellite thermal design, a
new simple thermal model which can model LAPAN-A3 thermal characteristic
accurately is needed.

Conventional thermal analysis requires accurate calculations of many variable
which results in increased complexity. Meanwhile, data-driven approaches in
solving satellite thermal problem are becoming increasinly common to reduce the
complexity and number of variable calculations needed in thermal modelling.
Thus, a semi-empirical approach which uses empirical telemetry data and
observations of the satellite to simplify the theoretical calculations of
satellite thermal equation hopefully can result in a quicker and easier thermal
modelling process.

In this paper, a semi-empirical 7-node thermal model of LAPAN-A3 satellite is
developed with machine learning method using linear regression approach. The
model is trained and tested with satellite data for the observation period of
19 and 20 May 2018 to solve the unknown variables in LAPAN-A3 satellite thermal
equation in order to predict the satellite nodes' temperature change. Initial
evaluation shows that the thermal model is generally able to predict LAPAN-A3
node temperature changes and has potential usage in real-life satellite
development. Even though the model can still be improved upon, it may serve as
a basis for future satellite thermal model.

\vspace{1.0cm}
\noindent 
Keywords : thermal model, satellite, machine learning, linear regression, LAPAN-A3 
